
\begin{center}
  \textbf{LIST OF SYMBOLS, ABBREVIATIONS AND NOMENCLATURE} 
\end{center}
\addcontentsline{toc}{chapter}{List of Symbols, Abbreviations}

\begin{itemize}
  \item[] \textbf{ECG}  : Electrocardiogram
  \item[] \textbf{EEG}  : Electroencephalogram
  \item[] \textbf{CVDs} : Cardiovascular Diseases
  \item[] \textbf{DIY}  : Do It Yourself
  \item[] \textbf{AD8232} : Bioinstrumentation Amplifier
  \item[] \textbf{DSO}  : Digital Storage Oscilloscope
  \item[] \textbf{MCU}  : Microcontroller Unit
  \item[] \textbf{Wi-Fi} : Wireless Fidelity
  \item[] \textbf{HTTP} : Hypertext Transfer Protocol
  \item[] \textbf{UI}   : User Interface
  \item[] \textbf{API}  : Application Programming Interface
  \item[] \textbf{ESP8266} : Wi-Fi Module
  \item[] \textbf{RC Filter} : Resistor-Capacitor Filter
  \item[] \textbf{DNS}  : Domain Name System
  \item[] \textbf{IoT}  : Internet of Things
\end{itemize}

\vspace{0.5cm}

\begin{center}
  \textbf{Technical Terms and Concepts} 
\end{center}

\begin{itemize}
  \item[] \textbf{Bioinstrumentation} : Application of electronics and measurement techniques for physiological data.
  \item[] \textbf{Signal Amplification} : Increasing the amplitude of ECG signals.
  \item[] \textbf{Baseline Wander} : Low-frequency noise caused by body movements or respiration.
  \item[] \textbf{Electromagnetic Interference (EMI)} : Disturbances from external electromagnetic sources.
  \item[] \textbf{WebSocket Protocol} : Real-time full-duplex communication channel.
  \item[] \textbf{Telemedicine} : Technology-based remote medical diagnostics and monitoring.
  \item[] \textbf{Graphical User Interface (GUI)} : Visual interface for user interaction.
  \item[] \textbf{Sinoatrial Node} : The natural pacemaker of the heart.
  \item[] \textbf{Real-Time Visualization} : Instant display of ECG signals for analysis.
  \item[] \textbf{Motion Artifacts} : Signal distortions caused by physical movements.
\end{itemize}

\vspace{0.5cm}

\begin{center}
  \textbf{Design Elements} 
\end{center}

\begin{itemize}
  \item[] \textbf{Spiral Copper Electrodes} : Custom reusable electrodes for ECG acquisition.
  \item[] \textbf{Low-Cost Healthcare Technology} : Affordable solutions for underserved areas.
  \item[] \textbf{Noise Filtering} : Removing unwanted signals from ECG data.
  \item[] \textbf{Single-Lead ECG} : Measuring electrical activity from one point on the body.
  \item[] \textbf{Precision Filters} : High-pass and low-pass filters for signal processing.
  \item[] \textbf{Wireless Data Transmission} : Sending ECG data via Wi-Fi.
  \item[] \textbf{Voltage Per Division (Volt/Div)} : Scaling unit for voltage on an oscilloscope.
  \item[] \textbf{Time Per Division (Time/Div)} : Scaling unit for time on an oscilloscope.
\end{itemize}

\vspace{0.5cm}

\begin{center}
  \textbf{Advanced and Future Concepts} 
\end{center}

\begin{itemize}
  \item[] \textbf{AI-Driven Analytics} : Artificial Intelligence for automated diagnostics.
  \item[] \textbf{Health Equity} : Ensuring equal access to medical resources.
  \item[] \textbf{Signal Processing} : Techniques for improving signal quality.
  \item[] \textbf{Remote Monitoring} : Analyzing health data from a distance.
  \item[] \textbf{Data Visualization Algorithms} : Computational methods for graphical data display.
\end{itemize}
